Covariate analysis of ROSMAP reprocessed counts (with CQN normalisation and covariates adjusted)

### 2017-06-21 code/Rmd/ROSMAP_REPROCESSED.Rmd
Minor modifications

tmp = COVARIATES %>%
  group_by(Diagnosis, cogdx) %>%
  summarise(count = n()) %>%
  spread(Diagnosis, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

@@

# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq (Normalised)", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)
synChangeEntityACL(CODE@properties$id, new.racl)

@@

# Delete folder acl
synDeleteEntityACL(CODE@properties$id)

>>>>

tmp = COVARIATES %>%
  dplyr::group_by(Diagnosis, cogdx) %>%
  dplyr::summarise(count = n()) %>%
  tidyr::spread(Diagnosis, count)
```
Processing `r dim(PROCESSED_COUNTS$filteredExprMatrix)[1]` genes in `r dim(PROCESSED_COUNTS$filteredExprMatrix)[2]` samples

@@

# Code
CODE <- Folder(name = "ROSMAP Reprocessed RNASeq (Normalised)", parentId = parentId)
annotations(CODE) = all.annotations
CODE <- synStore(CODE)
old.acl = synGetEntityACL(CODE@properties$id)
synChangeEntityACL(CODE@properties$id, new.racl)

@@

# Delete folder acl
synChangeEntityACL(CODE@properties$id, old.acl@resourceAccess)
